\section{Conclusion}
\label{sec:conclusion}

This paper contributes an open, reproducible firm-level microsimulation for
analysing the UK VAT registration threshold, released in full---including its
synthetic-data generator---for replication. The framework assembles four
components: a synthetic firm dataset built from ONS business-structure counts and
calibrated to HMRC VAT aggregates; a static costing of threshold-location and
schedule-shape reforms; a reduced-form bunching estimator; and a
\citet{klevenwaseem2013} notch model whose \emph{exact dominated region}
characterises the distortion the threshold imposes and how each reform changes it.
Its value is as usable policy infrastructure rather than a structural
identification result: I make no claim to recover policy-invariant firm
primitives, unlike \citet{garicano2016} and \citet{gourioroys2014}, which identify
such primitives at a size threshold. The analysis is anchored to the 2023--24
data year, in which the statutory threshold was \pounds85{,}000.
Table~\ref{tab:summary} collects the headline objects.

\begin{table}[t]
\centering
\caption{Summary of headline estimates. This table consolidates results reported
and defined in the body sections cross-referenced below; it is a reference summary,
not a new analysis. All quantities refer to the \pounds85{,}000 data-year baseline.
Static revenue figures are 2025--26.}
\label{tab:summary}
\small
\begin{tabular}{@{}llll@{}}
\toprule
Object & Symbol / definition & Value & Source \\
\midrule
\multicolumn{4}{@{}l}{\textit{Reduced-form bunching (\pounds85k data year)}} \\
Bunching ratio (geometry, \emph{not} an elasticity) & $b=\Delta y^{*}/y^{*}$ & $0.060$ & \S\ref{sec:bunching} \\
Aggregate displaced share & $\Pi$ & $0.211$ & \S\ref{sec:bunching} \\
Bunching-implied turnover elasticity (descriptive) & $\varepsilon$ (notch width) & $\approx 0.45$ & \S\ref{sec:bunching} \\
\midrule
\multicolumn{4}{@{}l}{\textit{Static costing and structural distortion}} \\
Static cost, \pounds85k to \pounds90k anchor & --- & $\approx-\pounds175$m & \S\ref{sec:static} \\
Static sweep, \pounds90k baseline & per \pounds5k step & $\sim\pounds150$--$220$m & Table~\ref{tab:static_revenue} \\
Dominated region (misallocation zone) & $a=T^{*}\tau/(1-\tau)$ & \pounds21{,}250 & \S\ref{ssec:dominated} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Findings.} First, \emph{the pipeline reproduces HMRC's static costing}.
My static costing of the real \pounds85{,}000 to \pounds90{,}000 threshold move
agrees with HMRC's published figures to within \pounds1m in 2025--26, and a
threshold sweep (Table~\ref{tab:static_revenue}) shows that moving the threshold is
approximately linear in revenue and adequately costed by a static calculation. This
is the validation anchor for the rest of the framework.

Second, \emph{the behavioural response at the notch is modest}. Firms bunch below
the threshold---a bunching ratio $b=0.060$, which once normalised to the
\citet{liuetal2021} excess-bunching statistic is of the same order as their
estimate. The bunching-implied turnover elasticity ($\approx 0.45$ from the notch
width) is modest, but I report it descriptively rather than as a structural
estimate: \citet{liuetal2021} decline to convert their bunching mass into an
elasticity at a notch, and a turnover notch confounds an output-supply response
with a demand-side one, so the number is an upper envelope rather than a
welfare-sufficient statistic.

Third, \emph{the structural notch model characterises the distortion exactly}. The
notch creates a dominated region of width $a=T^{*}\tau/(1-\tau)=\pounds21{,}250$, a
pure misallocation zone in which no firm optimally locates. This object is exact: it
depends on $\tau$ and $T^{*}$ alone, independent of the cost specification, the
returns-to-scale parameter $\alpha$, and any smoothing parameter, and it is the
structural counterpart of the missing mass measured just above the threshold. It is
the clean, robust index of the distortion the threshold imposes.

Fourth, \emph{I cost a menu of schedule reforms statically and state exactly how
each changes that distortion}. Re-applying each candidate schedule to the fixed
turnover distribution (Section~\ref{ssec:schedule_costs}) gives static revenue
effects of \(-\)\pounds374m for raising the threshold to \pounds100{,}000,
\(-\)\pounds335m for a graduated taper over $[\pounds85\text{k},\pounds105\text{k}]$,
and \(-\)\pounds357m and \(-\)\pounds178m for $10\%$ and $15\%$ banded reduced rates.
The dominated region responds analytically: raising the threshold relocates the
\pounds21{,}250 zone unchanged, a $10\%$ band shrinks it to \pounds9{,}444, a $15\%$
band to \pounds15{,}000, and a graduated taper removes it altogether. These are the
two robust objects---the static cost and the exact change in the misallocation
zone---that I report for each reform.

\paragraph{Limitations.} The model is a \emph{turnover-tax-notch approximation},
and this is its first-order limitation. It
treats VAT as a cost on turnover, whereas real VAT is levied on value added with
input reclaim, and roughly half of below-threshold firms register
\emph{voluntarily} because reclaim outweighs the output liability---the central fact
in \citet{liuetal2021}. The effective notch is therefore smaller (and, for
net-reclaim firms, can reverse sign) than my flat treatment implies. The microdata
are \emph{synthetic}---ONS business-structure counts calibrated to HMRC aggregates---
so agreement with HMRC totals is a consistency check, not external validation. The
analysis is \emph{partial-equilibrium}, abstracting from VAT pass-through into prices
\citep{benedek2015, belloncopestake2022}. And while the dominated-region distortion
measure is exact and analytic, any \emph{behavioural} revenue or distributional
magnitudes from re-solving firm behaviour would be parameter-sensitive (to the
smoothing parameter $k$ and the re-optimisation window), which is why I headline the
static costs and the analytic distortion measure rather than re-optimised numbers.

\paragraph{Future work.} The static reform costs and the analytic dominated-region
results are robust, but two natural extensions remain. First, a fuller
\emph{behavioural} treatment that headlines re-optimised revenue and distributional
magnitudes from re-solving firm behaviour under each schedule. Such an exercise
requires calibrating firm-level cost parameters and a turnover elasticity, and the
resulting magnitudes are sensitive to the smoothing parameter $k$ and the
re-optimisation window, so I leave a disciplined treatment to future work. Second, a full \emph{welfare/MVPF analysis} that models value added and
input reclaim would convert the dominated-region distortion measure into the
cost--benefit terms policy needs, and support the design of \emph{revenue-neutral}
schedule variants that neutralise the notch at no net fiscal cost. Modelling
\emph{voluntary registration}
and the input-VAT margin explicitly would let the framework represent the full UK
VAT population rather than the consumer-facing subpopulation it currently best
describes. Allowing sector heterogeneity and linking the microdata to
\citet{policyengine} would refine both the bunching estimates and any
counterfactuals. Above all, \emph{validation against administrative firm-level data}
would replace the present internal-consistency checks with genuine out-of-sample
tests.
