\section{The VAT Notch and Its Dominated Region}
\label{sec:model}

The reduced-form evidence in Section~\ref{sec:bunching} establishes that firms
respond to the VAT registration notch. To characterise that notch precisely I
set out its firm-level structure, following the framework of
\citet{klevenwaseem2013}, \citet{saez2010}, and \citet{kleven2016}, as applied
to UK VAT by \citet{liuetal2021}. The UK registration threshold is a
\emph{notch}, not a kink: once turnover crosses the threshold the firm becomes
liable for VAT on its \emph{entire} turnover, not merely on the increment above
it. I model this notch exactly. The section's central deliverable is the notch's
\emph{dominated region}---the exact, model-free measure of the distortion the
threshold imposes (Section~\ref{ssec:dominated}), whose analytic response to each
schedule reform complements the static reform costs of
Section~\ref{ssec:schedule_costs}. The dominated region is the robust, headline
structural object: it depends on the rate and threshold alone and is therefore
exact. A behavioural re-optimisation of firms under counterfactual schedules---a
forward solve that prices the response in turnover to reforms the data never
observe---would require additional, parameter-sensitive assumptions about the
firm's technology and elasticity, and I leave that dynamic layer to future work.

\paragraph{Scope: a turnover-tax notch.} The structure here taxes \emph{turnover}.
Real VAT is levied on \emph{value added} with input-tax reclaim, and a substantial
share of below-threshold firms register voluntarily to recover input VAT
\citep{liuetal2021}. My treatment abstracts from input reclaim and voluntary
registration: it is a turnover-tax-notch approximation. This is a scope limitation
I state up front; it bounds the welfare claims I make and is one I return to in the
concluding discussion.

\subsection{The firm's problem with a VAT notch}

Each firm $i$ chooses turnover $y_i$ to maximise after-tax profit. Let $c_i(y_i)$
denote the cost of producing turnover $y_i$, $T^{*}$ the registration threshold,
and $\tau$ the standard VAT rate. Because VAT applies to the firm's entire
turnover once it registers, after-tax revenue is discontinuous and profit is
\begin{equation}
  \pi_i(y_i) \;=\;
  \begin{cases}
    \;y_i - c_i(y_i), & y_i < T^{*} \quad \text{(unregistered)},\\[4pt]
    \;(1-\tau)\,y_i - c_i(y_i), & y_i \ge T^{*} \quad \text{(registered)}.
  \end{cases}
  \label{eq:firm-problem}
\end{equation}
At $T^{*}$ after-tax revenue falls discretely by $\tau\,T^{*}$: a firm
that nudges its turnover from just below to just above the threshold loses
$\tau\,T^{*}$ of net revenue on turnover it was already earning. With the
standard rate $\tau=0.20$ and threshold $T^{*}=\pounds85{,}000$ this discrete
drop is $\tau\,T^{*}=\pounds17{,}000$. This drop---absent from a kink, where only
the \emph{marginal} rate changes at the threshold while average liability moves
continuously---is the defining feature of a notch and the source of the bunching
documented in Section~\ref{sec:bunching}. It is what makes locating just below
the cutoff strictly attractive and creates the empty band derived in
Section~\ref{ssec:dominated}.

\subsection{The dominated region}
\label{ssec:dominated}

The notch creates a range of turnover just above $T^{*}$ that \emph{no} firm
chooses, because every point in it yields strictly lower profit than locating at
$T^{*}$. A firm at the threshold earns net revenue $T^{*}$; a registered firm at
$T^{*}+a$ earns $(1-\tau)(T^{*}+a)$. Equating the two---the cost difference
across this narrow band is negligible---the upper edge of the dominated region is
\begin{equation}
  (1-\tau)\,(T^{*}+a) \;=\; T^{*}
  \quad\Longrightarrow\quad
  a \;=\; T^{*}\,\frac{\tau}{1-\tau} .
  \label{eq:dominated}
\end{equation}
This is the Kleven--Waseem dominated-region width \citep{klevenwaseem2013}. At
my parameters it gives $a = \pounds85{,}000\times 0.20/0.80 = \pounds21{,}250$,
so the dominated region is
$(T^{*},\,T^{*}+a)=(\pounds85{,}000,\ \pounds106{,}250)$. Two properties make
this $\sim\pounds21$k band the load-bearing analytic object of the paper. First,
it is \emph{exact}: it depends on $\tau$ and $T^{*}$ alone and is independent of
the cost specification, of any behavioural elasticity, and of any smoothing
parameter. Second, it is an order of magnitude wider than the $\sim\pounds1$k
region implied by a smoothed \emph{kink} approximation. The dominated region is
the structural counterpart of the missing mass measured just above the threshold
in Section~\ref{sec:bunching}: the reduced-form deficit and the model-free empty
band are the same object viewed two ways. The contrast with a smoothed-kink
approximation, and a robustness check that a smooth schedule reproduces this
width, are taken up in a separate robustness appendix.

\paragraph{How each reform changes the dominated region.} Because the width
$a=T^{*}\tau/(1-\tau)$ depends on the threshold and the rate alone, the effect of
each schedule reform of Section~\ref{ssec:schedule_costs} on this misallocation
zone is exact and follows directly from~\eqref{eq:dominated}, with no dependence on
the cost specification, any behavioural elasticity, or any simulated
re-optimisation. Raising the threshold to \pounds100{,}000 leaves the rate
unchanged and therefore \emph{relocates} the zone without altering its width: it
is the same \pounds21{,}250 band, transported to the new cutoff. A banded reduced
rate \emph{shrinks} the zone, because $a$ falls with $\tau$: at
$T^{*}=\pounds85{,}000$, lowering the band rate to $15\%$ cuts it to
$\pounds85{,}000\times0.15/0.85=\pounds15{,}000$, and to $10\%$ cuts it to
$\pounds85{,}000\times0.10/0.90=\pounds9{,}444$. A graduated taper has \emph{no}
notch and hence no dominated region: marginal net revenue declines smoothly through
the band rather than off a cliff, so the band of dominated turnover---and with it
the discrete incentive to suppress turnover---is removed entirely. The dominated
region is thus the paper's exact, model-free measure of the distortion the notch
imposes, and the analytic statement above is exactly how much of that distortion
each reform of Section~\ref{ssec:schedule_costs} removes.
