\subsection{Data construction detail}
\label{app:data}

Section~\ref{sec:data} describes the two-stage synthetic-population pipeline,
parameterised by the registration threshold, and its calibration to HMRC and ONS
aggregates. This appendix records the implementation detail deferred from that
account.

Each of the approximately $2.94$ million firm rows carries a turnover, an input
expenditure, a calibration weight, and a registration status; the weights are
chosen so the weighted totals reproduce the official targets while the population
sums to about $2.5$ million firms. Because the population is calibrated \emph{to} the HMRC aggregates,
agreement between my weighted outputs and those aggregates is a check of
\emph{internal consistency}, not external validation: any target used in
calibration is reproduced by construction. I therefore read the
$\sim\!90\%$ calibration accuracy, and the close match of the static
\pounds85{,}000\,\(\to\)\,\pounds90{,}000 costing to HMRC's published figures, as
consistency checks on the pipeline rather than out-of-sample tests of firm
behaviour.

The reported calibration score is a bounded summary statistic. For each
dimension I compute
\(\max\{0,1-\lvert \widehat{T}-T\rvert/\lvert T\rvert\}\), so a dimension missed
by more than 100 percent receives zero rather than a negative score. The headline
``overall'' number is the unweighted mean of the five dimensions used as
calibration targets---HMRC turnover bands, ONS population, employment bands,
HMRC sector counts, and VAT liability by turnover band. VAT liability by sector
is excluded from that mean and reported separately as an informational
diagnostic, because the current generator does not calibrate sector-specific
input/output VAT structure.

\paragraph{Counterfactual exclusion window and polynomial degree.} The no-VAT
counterfactual density of Section~\ref{sec:bunching} is fitted by polynomial
regression on the observed density outside a manipulation window around the
threshold. The baseline excludes $[T^{*}-15\text{k}, T^{*}+15\text{k}]$ and fits
a cubic. Widening the window guards against contamination of the counterfactual
by the behavioural response but reduces the data available for the fit; raising
the degree improves in-sample fit but risks over-fitting the tails. The
sensitivity of the excess-mass and bunching-ratio estimates to window width and
degree, with associated uncertainty, is reported in
Appendix~\ref{app:inference}.
