\subsection{Inference for the bunching estimator}
\label{app:inference}

This appendix documents the inference procedure for the reduced-form bunching
estimates of Section~\ref{sec:bunching}: the mass-conservation constraint
that disciplines the counterfactual density, the bootstrap that delivers
standard errors, the sensitivity of the estimates to the polynomial degree,
the exclusion window, and the effective wedge $\tau_{e}$, and a placebo test
demonstrating that the synthetic bunching is mechanical rather than behavioural.
All numbers reported here and in the calibration step are produced by the
released estimator (fixed seed, $B=200$ bootstrap replications), run on the
\pounds85{,}000 (2023--24) weighted synthetic firm data; the seed and $B$ are
fixed so the table is reproducible, and nothing is hardcoded as a result.

\subsubsection*{Mass-conservation constraint}

The canonical bunching estimator of \citet{saez2010}, \citet{klevenwaseem2013}
and \citet{chettyetal2011} imposes that the counterfactual density conserves
mass: every firm removed from above the threshold reappears as excess mass below
it. An unconstrained fit by plain polynomial OLS on bins outside a hand-set
window computes the excess mass $E$ (below $T^{*}$) and the missing mass
$\Delta_{R}$ (above $T^{*}$) \emph{independently}, with no guarantee that
$E = \Delta_{R}$ and no endogenous location of the marginal buncher.

I impose the constraint in two ways. First, the counterfactual polynomial in
$(y-T^{*})$ is fit by an iterated weighted least-squares procedure in which the
density of the bins above the excluded region is rescaled until the fitted
counterfactual integrates to the \emph{observed} total mass over the estimation
range $[\pounds20\text{k},\pounds140\text{k}]$. This forces the bunching mass to
be reabsorbed into the counterfactual rather than discarded. The regressor is
normalised to $[-1,1]$ for numerical stability of the high-degree Vandermonde
basis. Second, the upper edge of the excluded (manipulation) region---the
\emph{marginal buncher} $y_{R}$---is located \emph{endogenously} by integrating
the missing mass upward from $T^{*}$ until cumulative missing mass above equals
cumulative excess mass below,
\[
  \int_{T^{*}}^{y_{R}} \bigl[f^{\mathrm{cf}}(y)-f^{\mathrm{obs}}(y)\bigr]_{+}\,dy
  \;=\;
  \int_{T^{*}-W}^{T^{*}} \bigl[f^{\mathrm{obs}}(y)-f^{\mathrm{cf}}(y)\bigr]_{+}\,dy
  \;=\; E ,
\]
rather than being fixed at an arbitrary window edge. The excess turnover span of
the marginal buncher, $\Delta y^{*}=y_{R}-T^{*}$, is then used by the
notch-width elasticity.

Imposing the constraint matters because the unconstrained fit grossly violates
adding-up: it delivers $E=7{,}820$ but $\Delta_{R}=16{,}524$, whereas the
constrained estimator returns $E=8{,}712$ and $\Delta_{R}=9{,}214$, which agree
to within sampling noise. Imposing the constraint thus reconciles the excess
mass below the threshold with the missing mass above it, which the
unconstrained estimator computes independently and which would otherwise diverge
by roughly a factor of two; the resulting movement in the headline estimates is
reported in the calibration step.

\subsubsection*{Bootstrap standard errors}

I compute standard errors by a firm-level bootstrap. In each of $B=200$
replications I draw $n$ firms with replacement from the estimation sample, with
draw probabilities proportional to the survey weight, re-bin the resampled firms
into \pounds1{,}000 bins, and re-run the entire estimator---counterfactual fit,
marginal-buncher location, and all downstream statistics---on the replicate. The
standard error of each statistic is the standard deviation of its bootstrap
distribution, and the $95\%$ confidence interval is the $2.5$th--$97.5$th
percentile interval. Resampling firms (rather than residuals) propagates both
sampling variation and the variation induced by re-binning. Table~\ref{tab:boot}
reports the results.

\begin{table}[t]
\centering
\caption{Bootstrap inference, \pounds85{,}000 data ($B=200$ firm resamples).}
\label{tab:boot}
\begin{tabular}{lrrr}
\hline
Statistic & Point & Std.\ error & 95\% CI \\
\hline
Bunching ratio $b$              & $0.060$ & $0.005$  & $[0.050,\ 0.068]$ \\
Excess mass $E$                 & $8{,}712$ & $662$  & $[7{,}920,\ 10{,}516]$ \\
Substitution elasticity $\sigma$ & $4.85$ & $0.12$  & $[4.58,\ 5.08]$ \\
Displaced share $\Pi$           & $0.211$ & $0.005$ & $[0.200,\ 0.219]$ \\
Notch-width elasticity (median) & $0.448$ & $0.027$ & $[0.405,\ 0.496]$ \\
Marginal-buncher elasticity     & $0.657$ & $0.082$ & $[0.510,\ 0.821]$ \\
\hline
\end{tabular}
\end{table}

\subsubsection*{Non-identification: the elasticities are not behavioural}

The bunching-implied elasticities in Table~\ref{tab:boot}---the notch-width
elasticity ($\approx 0.45$) and the marginal-buncher elasticity
($\approx 0.66$)---together with the CES substitution elasticity
$\sigma = 4.85$ are \emph{not} behaviourally identified on these data. The
synthetic firm population is calibrated to coarse aggregate HMRC turnover-band
counts, and the generator contains no firm location-choice: firms do not respond
to the threshold, so the excess mass below it is mechanical, inherited from the
density step in the calibration targets rather than from any behavioural
response (the placebo test below makes this precise). The elasticities are
therefore reported only as a record of what the estimator returns when applied
to these data; the paper draws no behavioural conclusion from them. This is an
instance of the general non-identification of bunching elasticities absent
exogenous variation or strong functional-form assumptions
\citep{blomquistetal2021, bertanhaetal2023}.

\subsubsection*{Sensitivity to polynomial degree and exclusion window}

Table~\ref{tab:degwin} maps the point estimates across a grid of polynomial
degree $\in\{5,6,7,8\}$ and symmetric exclusion window
$\in\{\pounds10\text{k},\pounds15\text{k},\pounds20\text{k},\pounds25\text{k}\}$.
The estimates are stable across the central cells (degree $6$--$7$, window
\pounds10--\pounds20k): the substitution elasticity stays in roughly
$4.4$--$5.7$ and the excess mass in $4{,}000$--$9{,}000$. The corner cells are
less reliable: at very wide windows ($\pounds25$k) the excluded region begins to
swallow genuine curvature in the density, the fitted counterfactual crosses the
observed density, and $b$ can turn slightly negative (so $\sigma$ is undefined);
at the lowest degree ($5$) the inflexible trend over-fits the bunching mass into
the counterfactual and inflates $b$. I therefore report the degree-$7$,
\pounds15k-window specification as the baseline, with the bootstrap CIs above
spanning the variation across the stable interior of the grid.

\begin{table}[t]
\centering
\caption{Degree $\times$ window sensitivity (point estimates), \pounds85{,}000
data. Cells with $b<0$ leave $\sigma$ undefined.}
\label{tab:degwin}
\begin{tabular}{llrrrr}
\hline
Degree & Window & $b$ & $E$ & $\sigma$ & Notch-width (median) \\
\hline
6 & \pounds10k & $0.077$ & $7{,}262$ & $5.42$ & $0.41$ \\
6 & \pounds15k & $0.045$ & $6{,}575$ & $4.99$ & $0.44$ \\
6 & \pounds20k & $0.015$ & $3{,}822$ & $4.21$ & $0.35$ \\
7 & \pounds10k & $0.091$ & $8{,}539$ & $5.07$ & $0.47$ \\
\textbf{7} & \textbf{\pounds15k} & $\mathbf{0.060}$ & $\mathbf{8{,}712}$ & $\mathbf{4.85}$ & $\mathbf{0.45}$ \\
7 & \pounds20k & $0.034$ & $7{,}313$ & $4.62$ & $0.43$ \\
\hline
\end{tabular}
\end{table}

\subsubsection*{Sensitivity to the effective wedge}

The CES substitution elasticity is recovered as $\sigma =
\ln(\mathrm{RR})/\ln(1+\tau_{e})$, where $\mathrm{RR}$ is the ratio of
counterfactual-to-observed above/below mass ratios. Because the wedge enters only
through $\ln(1+\tau_{e})$, $\sigma$ scales roughly as $1/\ln(1+\tau_{e})$ while
the displaced share $\Pi = 1-(1+\tau_{e})^{-\sigma}$ is essentially invariant
(it is pinned by $\mathrm{RR}$). On my data, $\tau_{e}=0.025$ gives
$\sigma=9.59$, $\tau_{e}=0.05$ gives $\sigma=4.85$, $\tau_{e}=0.075$ gives
$\sigma=3.28$, and $\tau_{e}=0.10$ gives $\sigma=2.49$, while $\Pi=0.211$
throughout. The magnitude of $\sigma$ is therefore conditional on $\tau_{e}$: I
adopt $\tau_{e}=0.05$ as a baseline effective registration wedge and report
$\Pi$, which is robust to it, as the policy-relevant displacement object.

\subsubsection*{Placebo test}

The non-identification of the bunching elasticities can be made precise with a
placebo test. The HMRC turnover-band targets to which the synthetic population
is calibrated are coarse: a single count for firms at or below \pounds85{,}000
and a single count for firms in \pounds85{,}000--\pounds150{,}000. The implied
average per-\pounds1{,}000 densities differ sharply across the threshold
($\approx 7{,}981$ firms/\pounds1{,}000 below versus $\approx 4{,}697$ above), so
the calibration target \emph{itself} contains a density step at exactly
\pounds85{,}000. Because the generator has no firm location-choice, any density
discontinuity in the synthetic population must be inherited from this stepped
target rather than produced by behaviour. The placebo removes the step and
re-runs the estimator. Table~\ref{tab:placebo} reports two variants: Placebo~A
reweights the existing synthetic firms so the per-\pounds1{,}000 density follows
a single smooth log-quadratic trend across the threshold (preserving total mass
over $[\pounds20\text{k},\pounds140\text{k}]$, no regeneration); Placebo~B
replaces the two HMRC band counts straddling \pounds85{,}000 with a split
implied by a single common per-\pounds1{,}000 density (no step in the target),
then re-runs the full generator and multi-objective calibration before
estimating.

\begin{table}[t]
\centering
\caption{Placebo test: removing the calibration density step collapses the
excess mass. \pounds85{,}000 data.}
\label{tab:placebo}
\begin{tabular}{lrrr}
\hline
Population & $b$ & $E$ & $b_{\mathrm{LLAT}}$ \\
\hline
Actual (control)                          & $+0.060$ & $8{,}712$ & $0.941$ \\
Placebo A (reweight density smooth)       & $-0.063$ & $0$       & $0.000$ \\
Placebo B (un-stepped HMRC band targets)  & $-0.016$ & $99$      & $0.010$ \\
\hline
\end{tabular}
\end{table}

When the density step is removed from the calibration target, the estimated
excess mass collapses from $8{,}712$ firms in the control to at most $\approx 99$
firms ($\approx 1\%$ of the control value) in Placebo~B, and to zero in
Placebo~A; the bunching ratio even turns slightly negative. This proves that the
synthetic bunching is inherited from the coarse HMRC turnover-band targets, not
from any firm behaviour, and confirms that the elasticities in
Table~\ref{tab:boot} are mechanical artefacts of the calibration rather than
behavioural parameters. The placebo is part of the released code and is fully
reproducible.
