% !TeX program = lualatex
% PREVIEW BUILD: Introduction -> Institutional background -> Data only.
% The full paper is main.tex; this file is a partial preview and is not the submission.
%----------------------------------------------------
\documentclass[12pt,letterpaper]{article}
\usepackage{YGTemplate}

% Title
%----------------------------------------------------
\title{A Firm-Level Microsimulation for VAT Policy Analysis\thanks{\textbf{Acknowledgements:} I thank Max Ghenis and Seyed Mahdi Hosseini for their great suggestions and helpful discussions.}}
\author{Vahid Ahmadi\thanks{Research Associate at PolicyEngine. Email: \href{mailto:vahid@policyengine.org}{vahid@policyengine.org}} \\[0.4cm] \normalsize PolicyEngine}
\date{{\footnotesize\textcolor{red}{Preliminary and Incomplete. Comments are welcome.}} \\ \vspace{0.3cm} \small \ifcase\month\or January\or February\or March\or April\or May\or June\or July\or August\or September\or October\or November\or December\fi\ \the\year}

% Main document
%------------------------------------------------------
\begin{document}
\maketitle

\begin{abstract}
I present an open, reproducible firm-level microsimulation for pricing reforms to the UK VAT registration threshold, released in full---including its synthetic data generator---as open-source code. The threshold is a \emph{notch}: once turnover crosses \pounds85{,}000, 20\% VAT falls due on a firm's entire turnover rather than only the excess, creating an incentive to bunch below. I build synthetic firm-level records from ONS business-structure counts (sector $\times$ turnover band $\times$ employment), calibrate them to HMRC VAT statistics for 2023--24, and apply three tools: a static costing of threshold-location reforms, a reduced-form bunching estimator, and a calibrated Kleven--Waseem notch model for schedule-shape reforms the reduced form cannot price. I treat the model as a turnover-tax-notch approximation for consumer-facing, limited-reclaim firms, abstracting from input reclaim and voluntary registration. Static costing reproduces HMRC's published figure for the \pounds85{,}000 to \pounds90{,}000 reform ($-$\pounds175m versus $-$\pounds185m in 2025--26). Behavioural responses are small: bunching ratio $b\approx0.061$; median local turnover elasticity $\approx0.17$. I report each reform's static cost and how much of the \pounds21{,}250 dominated region it removes: raising the threshold to \pounds100k ($-$\pounds374m) leaves the \pounds21{,}250 zone, relocated; a banded 10\% reduced rate ($-$\pounds357m) reduces it to \pounds9{,}444; a 15\% reduced rate ($-$\pounds178m) reduces it to \pounds15{,}000; and a graduated taper over $[\pounds85\text{k},\pounds105\text{k}]$ ($-$\pounds335m) removes it.
\end{abstract}

\vspace{0.3cm}
\noindent\textbf{Keywords:} value-added tax, microsimulation, tax notch, policy

\newpage
\input{Sections/intro}
\input{Sections/background}
\input{Sections/data}
\input{Sections/static}

\newpage
\bibliographystyle{econ}
{\small \bibliography{references}}

\end{document}
